\speculake: Hiding Malware in Speculative Execution

### 2018-12-13 paper/figures.tex
updated figure 3 and associated caption

\newcommand{\FigSpecMeasureNP}{
\begin{figure*}[t]
     \centering
        \includegraphics[width=0.9\textwidth]{figures/Speculative_measurements_no-parity.png}
        \caption{\textbf{Speculative limits}\,---\,%
    To find the number of instructions we can execute speculatively, we placed a speculative load
    after an increasing number of instructions, and measured the fraction of times the load
    was subsequently in cache. However, more complex instructions
    have stricter constraints, generally corresponding to the number of $\mu$-ops that an instruction
    comprises. We find that we can execute up to 220 instructions 
    speculatively, which corresponds with the size of the CPU's reorder buffer (ROB). We measure 
    the ROB size by timing two cache accesses with a variable number of 
    instructions between them. The step in cycles around 220 instructions indicates that the 
    second cache access was pushed out of the ROB defining an upper limit on size.  }
    \label{fig:spec-capacity-np}
\end{figure*}
}

>>>>

\newcommand{\FigSpecMeasureNP}{
\begin{figure*}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/Speculative_measurements_no-parity.png}
    \caption{\textbf{Speculative limits}\,---\,%
    To find the number of instructions we can execute speculatively we placed a signal gadget
    after an increasing number of instructions and measured the fraction of times the 
    loaded value was subsequently in cache. However more complex instructions have stricter 
    constraints applied at two limits that we have identified, cache latency cycle limitation, and 
    the CPU's reorder buffer~(ROB) size as measured by instruction $\mu$-ops. We find that the
    hit fraction for instructions with a ratio of cycle latency to $\mu$~ops greater than 1 undergo a
    steep drop to \~0.1 hit fraction before falling definitively to 0. The drop in hit fraction 
    indicates that the duration of the test in cycles is beyond the fist step in cache latency as shown in 
    Figure~\ref{fig:cache-miss} (approx. 200 cycles). If the instruction sequence does not reach the 
    cycle count limit we see only a sharp drop in hit fraction to 0 indicating the limiting factor 
    is ROB size.  For example, the \texttt{idiv (r32)} instruction we identify 18 as the maximum number of 
    instruction limited by ROB (with ~15 instructions for signal gadget), with a soft limit of 
    12 instructions enforced by the cache latency cycle limitation. 
    We measure the ROB size by timing two cache accesses with a variable number of 
    instructions between them and note that this aligns with the measured maximum \texttt{nop} instrustions.
    }
    \label{fig:spec-capacity-np}
\end{figure*}
}
